Measurement and Probability in Fuzzy Quantum Theories

### 2017-01-24 prop.tex
prop.tex \section{Increasing the Measurement Resource} Simplify proof..

\begin{definition}\cite{gleason1957,CookeKeaneMoran1985,peres1995quantum,RichmanBridges1999,Hamhalter2013}~For
any quantum probability measure~$\mu$ on the Hilbert space of dimension
3, we can define its \emph{frame function}~$f:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$
by $f\left(\ket{\psi}\right)=\mu\left(\proj{\psi}\right)$. For a
quantum probability measure~$\mu_{\phi}^{B}$ induced by the Born
rule, its frame function is denoted by $f_{\phi}^{B}$.\end{definition}

\begin{lemma}\cite{gleason1957,CookeKeaneMoran1985,peres1995quantum,RichmanBridges1999,Hamhalter2013}~A
frame function~$f:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$ satisfies
the following properties:
\begin{itemize}
\item $f\left(\lambda\ket{\psi}\right)=f\left(\ket{\psi}\right)$ for any
$\ket{\psi}\in\mathbb{C}S^{2}$ and $\lambda\in\mathbb{C}S^{0}$.
\item For any orthonormal basis~$\left\{ \ket{\psi_{i}}\right\} _{i=1}^{3}$,
we have $1=\sum_{i=1}^{3}f\left(\ket{\psi_{i}}\right)$.
\end{itemize}
Conversely, if a function~$f:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$
satisfies the above properties, $f$ must be a frame function.\end{lemma}

\begin{definition}For any quantum IVPM~$\bar{\mu}$ on the Hilbert
space of dimension 3, we can define an \emph{interval-valued frame
function}~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$ by $\bar{f}\left(\ket{\psi}\right)=\bar{\mu}\left(\proj{\psi}\right)$.
The left-end and the right-end of an interval-valued frame function
are $f^{l}:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$ and $f^{r}:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$
satisfying $\bar{f}\left(\ket{\psi}\right)=\left[f^{l}\left(\ket{\psi}\right),f^{r}\left(\ket{\psi}\right)\right]$,
respectively. Also, if $f$ is the frame function of $\mu$, $\bar{f}$
is the interval-valued frame function of $\bar{\mu}$, and $\mu$
is in the core of $\bar{\mu}$, then we say $f$ is in the core of
$\bar{f}$, and denoted by $f\in\mathrm{core}\left(\bar{f}\right)$.\end{definition}

\begin{lemma}A interval-valued frame function~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$
satisfies the following properties:
\begin{itemize}
\item $\bar{f}\left(\lambda\ket{\psi}\right)=\bar{f}\left(\ket{\psi}\right)$
for any $\ket{\psi}\in\mathbb{C}S^{2}$ and $\lambda\in\mathbb{C}S^{0}$.
\item For any orthonormal basis~$\left\{ \ket{\psi_{i}}\right\} _{i=1}^{3}$,
we have $1\in\sum_{i=1}^{3}\bar{f}\left(\ket{\psi_{i}}\right)$ and
$\left[1,1\right]-\bar{f}\left(\ket{\psi_{i}}\right)\subseteq\bar{f}\left(\ket{\psi_{j}}\right)+\bar{f}\left(\ket{\psi_{k}}\right)$,
where $i$, $j$, and $k$ are any permutations among $1$, $2$,
and $3$.
\end{itemize}
Conversely, if a function~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$
satisfies the above properties, $\bar{f}$ must be an interval-valued
frame function.\end{lemma}\footnote{\yutsung{Verify the proof...}}

\begin{definition}For $\ket{\psi}=\alpha_{0}\ket{0}+\alpha_{1}\ket{1}+\alpha_{2}\ket{2}=\begin{pmatrix}\alpha_{0}\\
\alpha_{1}\\
\alpha_{2}
\end{pmatrix}$ and $\ket{\phi}=\beta_{0}\ket{0}+\beta_{1}\ket{1}+\beta_{2}\ket{2}=\begin{pmatrix}\beta_{0}\\
\beta_{1}\\
\beta_{2}
\end{pmatrix}$, their cross product is defined as follow: 
\[
\ket{\psi\times\phi}=\ket{\psi}\times\ket{\phi}=\begin{vmatrix}\alpha_{1}^{*} & \beta_{1}^{*}\\
\alpha_{2}^{*} & \beta_{2}^{*}
\end{vmatrix}\ket{0}+\begin{vmatrix}\alpha_{2}^{*} & \beta_{2}^{*}\\
\alpha_{0}^{*} & \beta_{0}^{*}
\end{vmatrix}\ket{1}+\begin{vmatrix}\alpha_{0}^{*} & \beta_{0}^{*}\\
\alpha_{1}^{*} & \beta_{1}^{*}
\end{vmatrix}\ket{2}\textrm{ ,}
\]
where $\begin{vmatrix}\alpha & \beta\\
\alpha' & \beta'
\end{vmatrix}=\alpha\beta'-\alpha'\beta$. Also, even if $\ket{\psi}$ and $\ket{\phi}$ are normalized, their
cross product~$\ket{\psi}\times\ket{\phi}$ need not be normalized
as usual. We will use $\ket{\psi}\times\ket{\phi}$ and $\frac{\ket{\psi}\times\ket{\phi}}{\left\Vert \ket{\psi}\times\ket{\phi}\right\Vert }$
interchanged when there is no confusion.\qed\end{definition}

>>>>

\begin{definition}\cite{gleason1957,peres1995quantum,RichmanBridges1999}~For
any quantum probability measure~$\mu$ on the Hilbert space of dimension
3, we can define its \emph{frame function}~$f:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$
by $f\left(\ket{\psi}\right)=\mu\left(\proj{\psi}\right)$. For a
quantum probability measure~$\mu_{\phi}^{B}$ induced by the Born
rule, its frame function is denoted by $f_{\phi}^{B}$.\end{definition}

\begin{lemma}\cite{gleason1957,peres1995quantum,RichmanBridges1999}~A
frame function~$f:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$ satisfies
the following properties:
\begin{itemize}
\item $f\left(\lambda\ket{\psi}\right)=f\left(\ket{\psi}\right)$ for any
$\ket{\psi}\in\mathbb{C}S^{2}$ and $\lambda\in\mathbb{C}S^{0}$.
\item For any orthonormal basis~$\left\{ \ket{\psi_{i}}\right\} _{i=0}^{2}$,
we have $1=\sum_{i=0}^{2}f\left(\ket{\psi_{i}}\right)$.
\end{itemize}
Conversely, if a function~$f:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$
satisfies the above properties, $f$ must be a frame function.\end{lemma}

\begin{definition}For any quantum IVPM~$\bar{\mu}$ on the Hilbert
space of dimension 3, we can define an \emph{interval-valued frame
function}~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$ by $\bar{f}\left(\ket{\psi}\right)=\bar{\mu}\left(\proj{\psi}\right)=\left[f^{l}\left(\ket{\psi}\right),f^{r}\left(\ket{\psi}\right)\right]$,
where $f^{l}:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$ and $f^{r}:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$
are the left-end and the right-end of $\bar{f}$, respectively. Also,
if $f$ is the frame function of $\mu$, $\bar{f}$ is the interval-valued
frame function of $\bar{\mu}$, and $\mu$ is in the core of $\bar{\mu}$,
then we say $f$ is in the core of $\bar{f}$, and denoted by $f\in\mathrm{core}\left(\bar{f}\right)$.\end{definition}

\begin{lemma}A interval-valued frame function~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$
satisfies the following properties:
\begin{itemize}
\item $\bar{f}\left(\lambda\ket{\psi}\right)=\bar{f}\left(\ket{\psi}\right)$
for any $\ket{\psi}\in\mathbb{C}S^{2}$ and $\lambda\in\mathbb{C}S^{0}$.
\item For any orthonormal basis~$\left\{ \ket{\psi_{i}}\right\} _{i=0}^{2}$,
we have $1\in\sum_{i=0}^{2}\bar{f}\left(\ket{\psi_{i}}\right)$ and
$\left[1,1\right]-\bar{f}\left(\ket{\psi_{i}}\right)\subseteq\bar{f}\left(\ket{\psi_{j}}\right)+\bar{f}\left(\ket{\psi_{k}}\right)$,
where $i$, $j$, and $k$ are any permutations among $0$, $1$,
and $2$.
\end{itemize}
Conversely, if a function~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$
satisfies the above properties, $\bar{f}$ must be an interval-valued
frame function.\end{lemma}
\begin{proof}
Given a quantum IVPM~$\bar{\mu}$, it is straightforward to verify
that its interval-valued frame function~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$
satisfies the above properties.

Conversely, given a function~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$
satisfying the above properties, consider $\bar{\mu}:\events\rightarrow\mathscr{I}$
defined by
\begin{itemize}
\item $\bar{\mu}(\mathbb{0})=\left[0,0\right]$ and $\bar{\mu}(\mathbb{1})=\left[1,1\right]$. 
\item For any $\ket{\psi}\in\mathbb{C}S^{2}$, we have $\bar{\mu}\left(\proj{\psi}\right)=\bar{f}\left(\ket{\psi}\right)$
and $\bar{\mu}\left(\mathbb{1}-\proj{\psi}\right)=\left[1,1\right]-\bar{f}\left(\ket{\psi}\right)$.
\end{itemize}
Since other conditions are trivial, we only need to verify 
\begin{equation}
\bar{\mu}\left(\sum_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(P_{i}\right)\label{eq:quantumIVPMconditions}
\end{equation}
 for any set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$.
First, if $\mathbb{0}$ or $\mathbb{1}$ is in $\left\{ P_{i}\right\} _{i=1}^{N}$,
the statement could be reduced to the case without $\mathbb{0}$,
or its trivial. Hence, we only need to discuss $\left\{ P_{i}\right\} _{i=1}^{N}$
containing 1- or 2-dimensional projectors. When $\left\{ P_{i}\right\} _{i=1}^{N}$
containing 2-dimensional projectors, the definition of $\bar{\mu}$
implies equation~(\ref{eq:quantumIVPMconditions}). When $\left\{ P_{i}\right\} _{i=1}^{N}$
only containing 1-dimensional projectors, the properties of $\bar{f}$
implies equation~(\ref{eq:quantumIVPMconditions}).
\end{proof}
\begin{definition}For $\ket{\psi}=\alpha_{0}\ket{0}+\alpha_{1}\ket{1}+\alpha_{2}\ket{2}=\begin{pmatrix}\alpha_{0}\\
\alpha_{1}\\
\alpha_{2}
\end{pmatrix}$ and $\ket{\phi}=\beta_{0}\ket{0}+\beta_{1}\ket{1}+\beta_{2}\ket{2}=\begin{pmatrix}\beta_{0}\\
\beta_{1}\\
\beta_{2}
\end{pmatrix}$, their cross product is defined as follow: 
\[
\ket{\psi\times\phi}=\ket{\psi}\times\ket{\phi}=\begin{vmatrix}\alpha_{1}^{*} & \beta_{1}^{*}\\
\alpha_{2}^{*} & \beta_{2}^{*}
\end{vmatrix}\ket{0}+\begin{vmatrix}\alpha_{2}^{*} & \beta_{2}^{*}\\
\alpha_{0}^{*} & \beta_{0}^{*}
\end{vmatrix}\ket{1}+\begin{vmatrix}\alpha_{0}^{*} & \beta_{0}^{*}\\
\alpha_{1}^{*} & \beta_{1}^{*}
\end{vmatrix}\ket{2}\textrm{ ,}
\]
where $\begin{vmatrix}\alpha & \beta\\
\alpha' & \beta'
\end{vmatrix}=\alpha\beta'-\alpha'\beta$. Also, even if $\ket{\psi}$ and $\ket{\phi}$ are normalized, their
cross product~$\ket{\psi}\times\ket{\phi}$ need not be normalized
as usual. We will use $\ket{\psi}\times\ket{\phi}$ and $\frac{\ket{\psi}\times\ket{\phi}}{\left\Vert \ket{\psi}\times\ket{\phi}\right\Vert }$
interchanged when there is no confusion.\qed\end{definition}
